Practical implications of HATEOAS on a bridge between LOD and SPARQL

### 2012-02-27 eswc-2012/workshop.tex
minor stuff
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@118 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

The HATEOAS constraint requires that the application can navigate from
one resources to another using the hypermedia links in the present
resource \emph{only}, it should not require any out-of-band
information to do so. Thus, a RESTful API should not require prior
knowledge of a URI structure, but it does not forbid it as long as the
same information can be gleened from the resources. Nor does it
require that all resources can be reached from any other resource. As
such, the constraint is not very strict, one could argue that as long
as there are some links, the API satisfies the HATEOAS constraint.

>>>>

\section*{BRAINDUMP STATUS}

@@

The HATEOAS constraint requires that the application can navigate from
one resources to another using the hypermedia links in the present
resource \emph{only}, it should not require any out-of-band
information to do so. Thus, a RESTful API should not require prior
knowledge of a URI structure, but one may define the API in terms of
URI structure as long as the same information can be gleened from the
resources. Nor does it require that all resources can be reached from
any other resource. As such, the constraint is not very strict, one
could argue that as long as there are some links, the API satisfies
the HATEOAS constraint.
